Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-09 programming23/artifact/main.tex
dockerfile

@@

@@

{ \newcommand{\labelbars}[1]{\begin{tabular}[t]{l@{}l} \raisebox{2ex}{\begin{tabular}[t]{r}\mnocheck{}\\\mnonstrict{}\\\mstrict{}\end{tabular}} & #1 \end{tabular}}
  \begin{tabular}[t]{cc}
    Type errors & Background errors \\
    \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{out/error-by-mode-te.pdf}}
    & \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{out/error-by-mode-fs.pdf}}
  \end{tabular}
}

@@

Output from \texttt{code/type-error-survival.rkt}
run on \texttt{code/type-error-survival-ss-*.rktd}:

\begin{tabular}{lr@{~}r@{~}rr@{~}r@{~}rr@{~}r@{~}r}
  & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
  & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} \\\hline
  TypeMismatch & {0} & {0} & {0} & {103} & {51} & {80} & {13} & {6} & {18} \\
  UnknownSymbol & {0} & {0} & {0} & {1992} & {438} & {1797} & {38} & {18} & {35} \\
  UnknownProperty & {0} & {0} & {0} & {256} & {156} & {208} & {16} & {18} & {22} \\
  NotATable & {0} & {0} & {0} & {4} & {1} & {5} & {2} & {0} & {1} \\
  CannotExtendTable & {0} & {0} & {0} & {6} & {8} & {1} & {0} & {0} & {1} \\
  OnlyTablesCanHaveMethods & {0} & {0} & {0} & {0} & {0} & {2} & {0} & {0} & {0} \\
  DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
  CountMismatch & {0} & {0} & {0} & {184} & {42} & {157} & {9} & {2} & {9} \\
  FunctionDoesNotTakeSelf & {0} & {0} & {0} & {3} & {4} & {1} & {0} & {0} & {0} \\
  OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
  UnknownRequire & {0} & {0} & {0} & {43} & {30} & {37} & {5} & {3} & {3} \\
  IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
  SyntaxError & {0} & {0} & {8290} & {0} & {0} & {1149} & {0} & {0} & {29} \\
  UnknownPropButFoundLikeProp & {0} & {0} & {0} & {20} & {17} & {13} & {0} & {0} & {0} \\
  GenericError & {0} & {0} & {0} & {177} & {47} & {149} & {5} & {0} & {8} \\
  CannotCallNonFunction & {0} & {0} & {0} & {12} & {2} & {13} & {1} & {0} & {1} \\
  ExtraInformation & {0} & {0} & {0} & {46} & {6} & {33} & {1} & {0} & {1} \\
  ModuleHasCyclicDependency & {0} & {0} & {0} & {9} & {5} & {8} & {0} & {0} & {0} \\
  IllegalRequire & {0} & {0} & {0} & {7} & {1} & {11} & {0} & {0} & {0} \\
  FunctionExitsWithoutReturning & {0} & {0} & {0} & {6} & {1} & {5} & {7} & {3} & {5} \\
  CannotInferBinaryOperation & {0} & {0} & {0} & {0} & {1} & {0} & {5} & {6} & {6} \\
  MissingProperties & {0} & {0} & {0} & {8} & {3} & {6} & {5} & {3} & {3} \\
  OptionalValueAccess & {0} & {0} & {0} & {21} & {45} & {15} & {4} & {2} & {4} \\
\end{tabular}

@@

\includegraphics[width=0.8\columnwidth]{out/error-count-nocheck-row--te-density-diff.pdf}

\includegraphics[width=0.8\columnwidth]{out/error-count-nonstrict-row--te-density-diff.pdf}

\includegraphics[width=0.8\columnwidth]{out/error-count-strict-row--te-density-diff.pdf}

@@

From reordered text output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}:

>>>>

Current errors in edit range = (14917 + 16007) = 30924

@@

There are 642 = (347598 - 346956) multi-mode sessions.

@@

{ \newcommand{\labelbars}[1]{\begin{tabular}[t]{l@{}l} \raisebox{2ex}{\begin{tabular}[t]{r}\mnocheck{}\\\mnonstrict{}\\\mstrict{}\end{tabular}} & #1 \end{tabular}}
  \begin{tabular}[t]{cc}
    Type errors & Background errors \\
    \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{out/error-by-mode-te.png}}
    & \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{out/error-by-mode-fs.png}}
  \end{tabular}
}

@@

Output from \texttt{code/type-error-survival.rkt}
run on \texttt{code/type-error-survival-ss-*.rktd}
and then sorted alphabetically:

\begin{tabular}{lr@{~}r@{~}rr@{~}r@{~}rr@{~}r@{~}r}
  & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
  & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} \\\hline
  CannotCallNonFunction & {0} & {0} & {0} & {12} & {2} & {13} & {1} & {0} & {1} \\
  CannotExtendTable & {0} & {0} & {0} & {6} & {8} & {1} & {0} & {0} & {1} \\
  CannotInferBinaryOperation & {0} & {0} & {0} & {0} & {1} & {0} & {5} & {6} & {6} \\
  CountMismatch & {0} & {0} & {0} & {184} & {42} & {157} & {9} & {2} & {9} \\
  DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
  ExtraInformation & {0} & {0} & {0} & {46} & {6} & {33} & {1} & {0} & {1} \\
  FunctionDoesNotTakeSelf & {0} & {0} & {0} & {3} & {4} & {1} & {0} & {0} & {0} \\
  FunctionExitsWithoutReturning & {0} & {0} & {0} & {6} & {1} & {5} & {7} & {3} & {5} \\
  GenericError & {0} & {0} & {0} & {177} & {47} & {149} & {5} & {0} & {8} \\
  IllegalRequire & {0} & {0} & {0} & {7} & {1} & {11} & {0} & {0} & {0} \\
  IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
  MissingProperties & {0} & {0} & {0} & {8} & {3} & {6} & {5} & {3} & {3} \\
  ModuleHasCyclicDependency & {0} & {0} & {0} & {9} & {5} & {8} & {0} & {0} & {0} \\
  NotATable & {0} & {0} & {0} & {4} & {1} & {5} & {2} & {0} & {1} \\
  OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
  OnlyTablesCanHaveMethods & {0} & {0} & {0} & {0} & {0} & {2} & {0} & {0} & {0} \\
  OptionalValueAccess & {0} & {0} & {0} & {21} & {45} & {15} & {4} & {2} & {4} \\
  SyntaxError & {0} & {0} & {8290} & {0} & {0} & {1149} & {0} & {0} & {29} \\
  TypeMismatch & {0} & {0} & {0} & {103} & {51} & {80} & {13} & {6} & {18} \\
  UnknownPropButFoundLikeProp & {0} & {0} & {0} & {20} & {17} & {13} & {0} & {0} & {0} \\
  UnknownProperty & {0} & {0} & {0} & {256} & {156} & {208} & {16} & {18} & {22} \\
  UnknownRequire & {0} & {0} & {0} & {43} & {30} & {37} & {5} & {3} & {3} \\
  UnknownSymbol & {0} & {0} & {0} & {1992} & {438} & {1797} & {38} & {18} & {35} \\
\end{tabular}

@@

\includegraphics[width=0.8\columnwidth]{out/error-count-nocheck-row--te-density-diff.png}

\includegraphics[width=0.8\columnwidth]{out/error-count-nonstrict-row--te-density-diff.png}

\includegraphics[width=0.8\columnwidth]{out/error-count-strict-row--te-density-diff.png}

@@

From reordered text output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}.
Here is the raw, unsorted output:
